More than one Author with different Affiliations

### 2012-04-23 paper/ms.tex
Added details of MCMC proposals

\subsection{Toy Model}
For the first implementation I wrote at NYU, I used the following model and
priors:
\begin{itemize}
\item $N \sim \textnormal{Uniform}(0, 1, 2, ..., 1000)$ \\
\item The parameters of the spatial
distribution: $\alpha = \left\{x_c, y_c, \sigma\right\}$ \\
\item The spatial distribution: $p(x_i, y_i | \alpha)\sim\mathcal{N}\left(
\texttt{mean}=(x_c, y_c), \texttt{covariance}=
\left(\begin{array}{cc}\sigma^2 & 0 \\ 0 & \sigma^2\end{array}\right)\right)$ \\
\item The luminosity function: $p(f_i | \beta) \sim
\textnormal{Exponential}\left(\texttt{mean}=\beta\right)$
\end{itemize}

@@

>>>>

\subsection{Toy Model}
For the first implementation I wrote at NYU, I used the following model and
priors:
\begin{itemize}
\item $N \sim \textnormal{Uniform}(0, 1, 2, ..., 1000)$ \\
\item The parameters of the spatial
distribution: $\alpha = \left\{x_c, y_c, \sigma\right\}$ \\
\item The spatial distribution: $p(x_i, y_i | \alpha)\sim\mathcal{N}\left(
\texttt{mean}=(x_c, y_c), \texttt{covariance}=
\left(\begin{array}{cc}\sigma^2 & 0 \\ 0 & \sigma^2\end{array}\right)\right)$ \\
\item Prior on $\alpha$: Uniform within image for $(x_c, y_c)$, logUniform for
$\sigma$ with max value $\sim$ image size.
\item The luminosity function: $p(f_i | \beta) \sim
\textnormal{Exponential}\left(\texttt{mean}=\beta\right)$ \\
\item Prior on $\beta$: logUniform with generous bounds.
\end{itemize}

@@

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$(\alpha, \beta)$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Move stars along with $\alpha$
\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Stars fixed, use logHastings
factor \\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, use
logHastings factor \\
$(x,y)$ & $(x,y) \to (x,y)+(\delta_x, \delta_y)$ & Can move $>1$ star.
Include prior via logH \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes. Include prior
via logH
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.}
\end{table}
